---
title: 'Direct/Indirect Speech Acts FTO' 
author: "Lena Warnke"
date: "2/11/2022"
output:
  pdf_document: default
  html_document: default
  word_document: default 
---
#note on the contrast coding: -.5 = declarative and statement, 0.5 = interrogative and question

```{r}
# Clean up variables

rm(list=ls()) 
source("do_or_load.R")
```

# Libraries

```{r, results='hide'}

library(remedy)
library(plyr)
library(dplyr)
library(lme4)
library(lmerTest)
library(ggplot2)
library(hrbrthemes)
library(tidyverse)
library(sjmisc)
library(sjPlot)
library(jtools)
library(interactions)
library(stringr)

# stan / bayes
library(rstan)
library(rstanarm)
library(bayesplot)
library(bayestestR)
library(BayesFactor)

#library(performance)

library(bridgesampling)
```

# Data loading

```{r}
setwd("/home/chas/Projects/Indirect-FTOs/")

ftodata <- read.csv("sentence_ftos.csv",
                    header=TRUE,
                    na.strings = c("NaN"))


ftodata$convo_num <- as.factor(ftodata$convo_num)
ftodata$speaker <- as.factor(ftodata$speaker)

```
# Aux function for model reporting of regression models

```{r}
# Auxiliary Summary function
# Summarizes the output (this code creates the output)

# Call function with STAN model as arg

## Indicate number of fixed effects, argument for the function
summary_stan_model<-function(mod,nfixefs=3){ #number of fixed effects
  samples_m1 <- as.data.frame(mod)
  nfixefs<-nfixefs + 1 ## to including intercept
  mns<-rep(NA,nfixefs)
  ci95<-matrix(rep(NA,nfixefs*2),ncol=2)
  for(i in 1:nfixefs){
    condnames<-colnames(samples_m1)[1:nfixefs]
    condnames[1]<-"Intercept"
    mns[i]<-round(mean(samples_m1[,i]),digits=4) 
    ci95[i,]<-round(quantile(probs=c(0.025,0.975),samples_m1[,i]),digits=4)
  }
  ## prob less than 0
  prob_less<-rep(NA,nfixefs)
  prob_more <-rep(NA,nfixefs)
  for(i in 1:nfixefs){
    prob_more[i]<-round(mean(samples_m1[,i]>0),digits=2)
    prob_less[i]<-round(mean(samples_m1[,i]<0),digits=2)
  }
  res<-as.data.frame(cbind(condnames,mns,ci95,prob_more, prob_less))
#  colnames(res)<-c("comparison","mean","lower","upper","P(b>0)", "P(b<0)")
  colnames(res)<-c(mod$formula,"mean","lower","upper","P(b>0)", "P(b<0)")
  return(res)
}
```

# Run Bayesian regression models

#Set sample size.

```{r}
SAMPLES <- 50000 #change back to 50000 at some point
options(mc.cores = parallel::detectCores())

```
# Full model

# Delete model files to force recompute, e.g. when sample size or data changed. (Disable with eval=false)

```{r, eval=false}

# model
file.remove("tmp/fto_.Rdata")
file.remove("tmp/eot_collapsed_length.Rdata")
file.remove("tmp/model_comparison.Rdata")
file.remove("tmp/no_condition.Rdata")
```

THE MODELS

#random intercepts only models

```{r, results='hide'}

#null model
message("Fitting Bayesian regression model null model.")
do_or_load("fto_null_model",
           stan_glmer(fto ~ (1|convo_num),
                      ftodata,
                      chains = 4,
                      iter = SAMPLES,
                      diagnostic_file = "null_model.csv", 
                      refresh = 0))
summary_fto_null_model <- summary_stan_model(fto_null_model, nfixefs = 1)

#main effect of sentence type

message("Fitting Bayesian regression model for sentence type")
do_or_load("fto_sentence_type",
           stan_glmer(fto ~ sentence_type + (1|convo_num), 
                      ftodata,
                      chains = 4,
                      iter = SAMPLES,
                      diagnostic_file = "fto_sentence_type.csv", 
                      refresh = 0))
summary_fto_sentence_type <- summary_stan_model(fto_sentence_type , nfixefs = 2)

#main effect of speech act
#switch model: switch

message("Fitting Bayesian regression model for switch.")
do_or_load("fto_speech_act",
           stan_glmer(fto ~ speech_act + (1|convo_num), 
                      ftodata,
                      chains = 4,
                      iter = SAMPLES,
                      diagnostic_file = "fto_speech_act.csv", 
                      refresh = 0))
summary_fto_speech_act <- summary_stan_model(fto_speech_act, nfixefs = 1)

#switch and condition model: switch, condition

message("Fitting Bayesian regression model for speech act and sentence type")
do_or_load("fto_speech_act_sentence_type",
           stan_glmer(fto ~ sentence_type + speech_act + (1|convo_num), 
                      ftodata,
                      chains = 4,
                      iter = SAMPLES,
                      diagnostic_file = "speech_act_sentence_type.csv", 
                      refresh = 0))
summary_fto_speech_act_sentence_type <- summary_stan_model(fto_speech_act_sentence_type, nfixefs = 3)

#sentence type and speech act interaction model

message("Fitting Bayesian regression model for speech act and sentence type interaction")
do_or_load("fto_speech_act_sentence_type_interaction",
           stan_glmer(fto ~ sentence_type*speech_act + (1|convo_num), 
                      ftodata,
                      chains = 4,
                      iter = SAMPLES,
                      diagnostic_file = "speech_act_sentence_type_interaction.csv", 
                      refresh = 0))
summary_fto_speech_act_sentence_type_interaction <- summary_stan_model(fto_speech_act_sentence_type_interaction, nfixefs = 5)
```

#Show summary.

```{r}

summary_fto_null_model
summary_fto_sentence_type
summary_fto_speech_act
summary_fto_speech_act_sentence_type
summary_fto_speech_act_sentence_type_interaction
```

Bayesian Model comparison

Using Quentin's bridge sampler


```{r, eval=FALSE}

#main effect of sentence type, no random slopes

message("Bayes Factor model comparison: main effect of condition")

do_or_load("model_comparison_sentence_type",
           bayesfactor_models(fto_sentence_type,
                              fto_null_model,
                              denominator = fto_null_model))
model_comparison_sentence_type
bayesfactor_inclusion(model_comparison_sentence_type)

#main effect of speech act

message("Bayes Factor model comparison: main effect of speech act")
do_or_load("model_comparison_speech_act",
           bayesfactor_models(fto_speech_act,
                              fto_null_model,
                              denominator = null_model))
model_comparison_speech_act
bayesfactor_inclusion(model_comparison_speech_act)

#comparing model with sentence type and speech act compared to model with just sentence type
message("Bayes Factor model comparison: adding switch to condition model")
do_or_load("model_comparison_sentence_type_speech_act",
           bayesfactor_models(fto_sentence_type,
                              fto_speech_act,
                              denominator = fto_sentence_type))
model_comparison_sentence_type_speech_act
bayesfactor_inclusion(model_comparison_sentence_type_speech_act)

#comparing model with and without interaction

message("Bayes Factor model comparison: interaction of sentence type and speech act")
do_or_load("model_comparison_interaction",
           bayesfactor_models(fto_sentence_type,
                              fto_speech_act_sentence_type_interaction,
                              denominator = fto_sentence_type))
model_comparison_interaction
bayesfactor_inclusion(model_comparison_interaction)

```